Music Perception: Pilot Accuracy Analysis

### 2021-01-25 analysis/analysis.Rmd
export judgements for teaching
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## 1. Summary
### All
```{r acc, echo = FALSE}
# individual
ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

@@

## 2. Teaching stimuli
### All
```{r item1, echo = FALSE}
# individual
ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data2 <- ind_data2[order(subjectNumber, Condition, Skill, MidFile)]

# all
subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
subset2[order(-Mean_Percent)]
```

@@

## 3. Performing stimuli
### All
```{r item2, echo = FALSE}
# individual
ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]

# all
subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
subset3[order(-Mean_Percent)]
```

@@

```{r export, include = FALSE}
order_data <- rbind(subset2, subset3)

# export
fwrite(order_data, file = "order_data.txt")
```

>>>>

## 1. Statistics
### All
```{r acc, echo = FALSE}
# individual
ind_data <- data[subjectNumber != 9, .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber)]
ind_data <- ind_data[order(subjectNumber)]

@@

## 2. Teaching stimuli
```{r item1, echo = FALSE}
# individual
ind_data2 <- data[subjectNumber != 9 & Condition == "teaching", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data2 <- ind_data2[order(subjectNumber, Condition, Skill, MidFile)]

# all
subset2 <- ind_data2[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
```

@@

## 3. Performing stimuli
```{r item2, echo = FALSE}
# individual
ind_data3 <- data[subjectNumber != 9 & Condition == "performing", .(N = .N, Sum = sum(Correct), Percent = (sum(Correct)/.N)*100), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data3 <- ind_data3[order(subjectNumber, Condition, Skill, MidFile)]

# all
subset3 <- ind_data3[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
```

@@

# Accuracy for each stimulus
```{r export, echo = FALSE}
accuracy_data <- rbind(subset2, subset3)
accuracy_data <- accuracy_data[order(MidFile)]
accuracy_data

# export
fwrite(accuracy_data, file = "accuracy_data.txt")
```

# Judged as "teaching" for each stimulus
```{r teaching, echo = FALSE}
data$Teaching <- 0
data[rating == "Yes"]$Teaching <- 1

# individual
ind_data4 <- data[subjectNumber != 9, .(N = .N, Sum = sum(Teaching)), by = .(subjectNumber, Condition, Skill, MidFile)]
ind_data4 <- ind_data4[order(subjectNumber)]

# all
subset4 <- ind_data4[, .(N = .N, Mean = mean(Sum), SD = sd(Sum), Mean_Percent = (mean(Sum))*100, SD_Percent = (sd(Sum))*100), by = .(Condition, Skill, MidFile)]
subset4 <- subset4[order(MidFile)]
subset4

# export
fwrite(subset4, file = "teaching_data.txt")
```
